\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-03-11 doc/manuscript.tex
minor ms edits

Ecological forecasts are typically made using either a space-for-time substitution approach based on models fit to spatial data or using dynamic models fit to time-series data. Our results demonstrate that these two approaches can make very different predictions about the future state of ecological systems. Which approach provides the most accurate forecasts depends on the forecast-horizon. In our simulations, time-series approaches performed best for short forecast horizons, whereas models based on spatial data made more accurate forecasts at long horizons. In addition, our simulations demonstrate extended transitional periods during which neither the time-series or the spatial approach was effective on its own. The challenge is determining what is ``short-term,'' what is ``long-term,'' and how to handle the many forecasts we need in ecology which fall in between. We have proposed that a weighted combination of the time-series and space-for-time approaches may produce better forecasts at these intermediate forecast horizons.

>>>>

Ecological forecasts are typically made using either a space-for-time substitution approach based on models fit to spatial data or using dynamic models fit to time-series data. \new{Empirical studies show that the environment-response relationships detected by these approaches frequently differ in magnitude and even sign \citep{lauenroth_long-term_1992,Oedekoven2017,Amburgey2018,kleinhesselink_response_2018}. Our simulations illustrate how such differences may arise and then lead to} very different predictions about the future state of ecological systems. Which approach provides the most accurate forecasts \new{likely} depends on the forecast-horizon. In our simulations, time-series approaches performed best for short forecast horizons, whereas models based on spatial data made more accurate forecasts at long horizons. In addition, our simulations demonstrate extended transitional periods during which neither the time-series or the spatial approach was effective on its own. The challenge is determining what is ``short-term,'' what is ``long-term,'' and how to handle the many forecasts we need in ecology which fall in between. We have proposed that a weighted combination of the time-series and space-for-time approaches may produce better forecasts at these intermediate forecast horizons.
